Freezing of a Weeks-Chandler-Anderson Fluid using classical Density Functional Theory

### 2020-12-04 papers/thesis-kirstie/thesis.tex
fixed typos

\begin{figure}
   \centering
   \includegraphics[height=8cm]{VaryWidthandVacancies.png}
   \caption{Shows an example set of Gaussian distribution number density 
   profiles $n(vec r)$ all with the same number density.
   with the same number density of one atom over the fixed volume.}
   \label{fig:Ensemble_vary}
\end{figure}

>>>>

\begin{figure}
   \centering
   \includegraphics[height=8cm]{VaryWidthandVacancies.png}
   \caption{Shows an example set of Gaussian distribution number density 
   profiles $n(\vec r)$ all with the same number density, n.}
   \label{fig:Ensemble_vary}
\end{figure}
